### 2013-06-08 doc/pgas13/flat-combining.tex
Related work and citations galore.

\paragraph{Sequential Consistency}
The sequential consistency guarantee is that within a task, operations will be in task order, so to enforce ordering between operations in different tasks, one task must perform an operation that another one can observe. An example is shown in Figure~\ref{fig:sync}.\TODO{make sync example}
The Grappa memory model follows the Data-Race-Free-0 Model (guaranteeing sequential consistency for data-race free programs). Being conservative, delegate operations block the calling worker until they have completed globally, ensuring they can be used for synchronization---delegate operations within a task are guaranteed to be globally visible in program order.
Because it is not immediately obvious that this distributed version of flat combining preserves sequential consistency, here we will make arguments for why it does.

>>>>

\paragraph{Sequential Consistency}
The sequential consistency guarantee is that within a task, operations will be in task order, so to enforce ordering between operations in different tasks, one task must perform an operation that another one can observe. An example is shown in Figure~\ref{fig:sync}.\TODO{make sync example}
The Grappa memory model is in the style of the C++ memory model~\cite{boehm:drf0,N2480,N2800} memory model (guaranteeing sequential consistency for data-race free programs). Being conservative, delegate operations block the calling worker until they have completed globally, ensuring they can be used for synchronization. As such, delegate operations within a task are guaranteed to be globally visible in program order.
Because it is not immediately obvious that this distributed version of flat combining preserves sequential consistency, here we will make arguments for why it does.

### 2013-06-08 doc/pgas13/grappa.tex
Overhaul of FC section.
Related work and citations galore.

\subsection{Aggregated Communication}
Communication in Grappa is achieved via \emph{active messages} in conjunction with bulk remote direct memory access (RDMA) operations. Various components of Grappa's runtime contribute different kinds of messages to move and modify remote data, perform synchronization, or spawn tasks. To make efficient use of the networks in high-performance systems, which perform better with larger messages (typically 64 KB), all communication in Grappa is sent through an aggregation layer that automatically accumulates messages to the same destination. When enough messages are ready to go to a particular destination node, they are serialized into a buffer and sent using RDMA.

>>>>

\subsection{Aggregated Communication}
Communication in Grappa is achieved via \emph{active messages}~\cite{vonEicken92} in conjunction with bulk remote direct memory access (RDMA)~\TODO{cite?} operations. Various components of Grappa's runtime contribute different kinds of messages to move and modify remote data, perform synchronization, or spawn tasks. To make efficient use of the networks in high-performance systems, which perform better with larger messages (typically 64 KB), all communication in Grappa is sent through an aggregation layer that automatically accumulates messages to the same destination. When enough messages are ready to go to a particular destination node, they are serialized into a buffer and sent using RDMA.

### 2013-06-08 doc/pgas13/intro.tex
Related work and citations galore.

The goal of partitioned global address space (PGAS) languages and runtimes is to provide the illusion of a single shared memory to a program that actually executes on a number of machines each with their own memory. This allows programmers to write their algorithms without needing to explicitly manage communication. Once the algorithm is correct, many techniques exist to help improve performance improving locality (spatial and temporal) and coarsening communication where possible. However, with this shared memory abstraction come all of the difficult concurrency issues that arise in physically-shared memory. Luckily, there exists a large body of work solving these issues in physically-shared memory which the PGAS community can leverage. The opportunity here is that, in a distributed setting, the costs of communication and synchronization operations are different, so different performance trade-offs will be made.

>>>>

The goal of partitioned global address space (PGAS)~\cite{upc:2005} languages and runtimes is to provide the illusion of a single shared memory to a program that actually executes on a number of machines each with their own memory. This allows programmers to write their algorithms without needing to explicitly manage communication. Once the algorithm is correct, many techniques exist to help improve performance improving locality (spatial and temporal) and coarsening communication where possible. However, with this shared memory abstraction come all of the difficult concurrency issues that arise in physically-shared memory. Luckily, there exists a large body of work solving these issues in physically-shared memory which the PGAS community can leverage. The opportunity here is that, in a distributed setting, the costs of communication and synchronization operations are different, so different performance trade-offs will be made.
